---
title: "Satellite_Comparison"
author: "Britta Themann"
date: "05.05.2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

## install packages
```{r}
# install.packages("ggplot2")
library(ggplot2)
# install.packages("svglite")
library(svglite)
```

## create satellite dataframe
```{r}
# load csv file
data <- read.csv("Satellite_Comparison_Source.csv")

# define column names
colnames(data) <- c("Satellite","Satellite Count","Instrument",
              "Band","Bandname","Band Purpose",
              "Wavelength [nm]","Bandwidth [nm]","Min Wavelength [nm]","Max Wavelength [nm]",
              "Spatial Resolution [cm].","Radiometric Resolution [bits].","Min Temporal Resolution [days]","Max Temporal Resolution [days]","X Image Extent [km]","Y Image Extent [km]","Type")
```

## Wavelength - Domain - Representation
UV
    < 435: UV - magenta
VIS
380 - 435: Violet - violet
435 - 500: Blue - royalblue
500 - 520: Cyan - cyan
520 - 565: Green - forestgreen
565 - 590: Yellow - darkgoldenrod1
590 - 625: Orange - orange
625 - 740: Red - red
NIR
740 - 1000: NIR - red3
SWIR
1000 - 2500: SWIR - TBD

## Band Comparison dataset preparation
```{r}
# limit dataset to NAOS domain
data.bc <- data[which(data$`Wavelength [nm]`< 1000),]

# add Color column
for (row in 1:nrow(data.bc)){
  if (data.bc$`Wavelength [nm]`[row] < 380){data.bc$Color[row] <- 'magenta'}
  else if (data.bc$`Wavelength [nm]`[row] >= 380 && data.bc$`Wavelength [nm]`[row] < 435){data.bc$Color[row] <- 'violet'}
  else if (data.bc$`Wavelength [nm]`[row] >= 435 && data.bc$`Wavelength [nm]`[row] < 500){data.bc$Color[row] <- 'royalblue'}
  else if (data.bc$`Wavelength [nm]`[row] >= 500 && data.bc$`Wavelength [nm]`[row] < 520){data.bc$Color[row] <- 'cyan'}
  else if (data.bc$`Wavelength [nm]`[row] >= 520 && data.bc$`Wavelength [nm]`[row] < 565){data.bc$Color[row] <- 'forestgreen'}
  else if (data.bc$`Wavelength [nm]`[row] >= 565 && data.bc$`Wavelength [nm]`[row] < 590){data.bc$Color[row] <- 'darkgoldenrod1'}
  else if (data.bc$`Wavelength [nm]`[row] >= 590 && data.bc$`Wavelength [nm]`[row] < 625){data.bc$Color[row] <- 'orange'}
  else if (data.bc$`Wavelength [nm]`[row] >= 625 && data.bc$`Wavelength [nm]`[row] < 740){data.bc$Color[row] <- 'red'}
  else {data.bc$Color[row] <- 'red3'}
}

# OPTIONAL for checking: add Domain column
# cuts <- c(0,380, 435, 500, 520, 565, 590, 625, 740, 1000)
# groups <- c("UV", "Violet", "Blue", "Cyan", "Green", "Yellow", 'Orange', 'Red', 'NIR')
# data.bc$Domain <- cut(data.bc$`Wavelength [nm]`, breaks = cuts, labels = groups, right = FALSE)
 
# overwrite color for Pan channels
data.bc$Color[data.bc$Bandname == 'Pan'] <- 'grey'

# fix Satellite order
data.bc$Satellite <- as.factor(data.bc$Satellite)
data.bc$Satellite <- factor(data.bc$Satellite, levels=c('NAOS','Pléiades Neo','WorldView-3','GeoEye-1','PlanetScope',
                                                        'Sentinel-2','Landsat-9','Sentinel-3'))

# subset VHR data
data.bc.vhr <- subset(data.bc, Type %in% 'VHR')

# subset MR data + NAOS
data.bc.mr <- rbind(subset(data.bc, Type %in% 'MR'),subset(data.bc, Satellite %in% 'NAOS'))
```

## create Band Comparison Plot (VHR+MR)
```{r}
# plot
plot.bc <- ggplot(data.bc, aes(Satellite, `Wavelength [nm]`))+
  
  # band visualization
  geom_errorbar(aes(ymin = `Min Wavelength [nm]`, ymax = `Max Wavelength [nm]`, group = Band, color=Color),
                position = position_dodge(1), size = 8, width = 0)+
  
  # labels
  geom_text(aes(label=Band, group= Band),  size=2,  alpha=0.8, color="black", fontface="bold", 
            position = position_dodge(1), check_overlap = F)+
 
  # color palette
  scale_color_identity()+
  
  # adjust wavelength axis
  scale_y_continuous(breaks = seq(300, 1000, by = 100))+
  
  
  geom_vline(xintercept=seq(1.5, length(unique(data.bc$Satellite))-0.5, 1), lwd=0.2, colour="black", linetype='dashed')+

  # flip x and y-axis
  coord_flip()+

  # title, axes and theme
  labs(title="Band Comparison of Optical EO Satellites")+
  theme_classic()+
  theme(plot.title = element_text(face="bold", size=14, hjust = 0.5),
        axis.title.x = element_text(face="bold", size=12),
        axis.title.y = element_text(face="bold", size=12),
        legend.title = element_text(face = "bold"),
        legend.position="none")

plot.bc
```

## create VHR Band Comparison Plot 
```{r}
# plot
plot.bc.vhr <- ggplot(data.bc.vhr, aes(Satellite, `Wavelength [nm]`))+
  
  # band visualization
  geom_errorbar(aes(ymin = `Min Wavelength [nm]`, ymax = `Max Wavelength [nm]`, group = Band, color=Color),
                position = position_dodge(1), size = 8, width = 0)+
  
  # labels
  geom_text(aes(label=Band, group= Band),  size=2,  alpha=0.8, color="black", fontface="bold", 
            position = position_dodge(1), check_overlap = F)+
 
  # color palette
  scale_color_identity()+
  
  # adjust wavelength axis
  scale_y_continuous(breaks = seq(300, 1000, by = 100))+
  
  
  geom_vline(xintercept=seq(1.5, length(unique(data.bc$Satellite))-0.5, 1), lwd=0.2, colour="black", linetype='dashed')+

  # flip x and y-axis
  coord_flip()+

  # title, axes and theme
  labs(title="Band Comparison of VHR Optical EO Satellites")+
  theme_classic()+
  theme(plot.title = element_text(face="bold", size=14, hjust = 0.5),
        axis.title.x = element_text(face="bold", size=12),
        axis.title.y = element_text(face="bold", size=12),
        legend.title = element_text(face = "bold"),
        legend.position="none")

plot.bc.vhr
```

## create MR Band Comparison Plot 
```{r}
# plot
plot.bc.mr <- ggplot(data.bc.mr, aes(Satellite, `Wavelength [nm]`))+
  
  # band visualization
  geom_errorbar(aes(ymin = `Min Wavelength [nm]`, ymax = `Max Wavelength [nm]`, group = Band, color=Color),
                position = position_dodge(1), size = 8, width = 0)+
  
  # labels
  geom_text(aes(label=Band, group= Band),  size=2,  alpha=0.8, color="black", fontface="bold", 
            position = position_dodge(1), check_overlap = F)+
 
  # color palette
  scale_color_identity()+
  
  # adjust wavelength axis
  scale_y_continuous(breaks = seq(300, 1000, by = 100))+
  
  
  geom_vline(xintercept=seq(1.5, length(unique(data.bc$Satellite))-0.5, 1), lwd=0.2, colour="black", linetype='dashed')+

  # flip x and y-axis
  coord_flip()+

  # title, axes and theme
  labs(title="Band Comparison of MR Optical EO Satellites")+
  theme_classic()+
  theme(plot.title = element_text(face="bold", size=14, hjust = 0.5),
        axis.title.x = element_text(face="bold", size=12),
        axis.title.y = element_text(face="bold", size=12),
        legend.title = element_text(face = "bold"),
        legend.position="none")

plot.bc.mr
```

## print Band Comparison plots
```{r}
ggsave(file=paste0("Band_Comparison.pdf"), plot=plot.bc, width=15, height=18)
ggsave(file=paste0("Band_Comparison.svg"), plot=plot.bc, width=15, height=18)
ggsave(file=paste0("Band_Comparison_VHR.pdf"), plot=plot.bc.vhr, width=15, height=10)
ggsave(file=paste0("Band_Comparison_VHR.svg"), plot=plot.bc.vhr, width=15, height=10)
ggsave(file=paste0("Band_Comparison_MR.pdf"), plot=plot.bc.mr, width=15, height=8)
ggsave(file=paste0("Band_Comparison_NR.svg"), plot=plot.bc.mr, width=15, height=8)
```

## title
```{r}

```
